MLExplain

### 2018-07-23 paper.tex
final tweaks

Fortunately the web interface is very simple. It is composed of some auxiliary
JavaScript files, the main JavaScript file -- \texttt{navig-driver.js} --
containing the logic of the application and the corresponding HTML page. The
only modified file is \texttt{navig-driver.js}. The resulting tool can be tested
online\footnote{\url{https://docteur-lalla.github.io/mlexplain/branch/master/driver.html}}
and is shown in Figure~\ref{fig:mlexplain}. The top-left panel shows the
interpreted, here a simple eval function using GADTs, with the state of the
program depicted on the right. The bottom panel shows the
interpreter, with its state below. One can see that at this point the
\texttt{eval} identifier is being evaluated, with the values of \texttt{r},
\texttt{l}, and \texttt{b} shown on the right.

\begin{figure*}
  \centering
  \includegraphics[width=14cm]{mlexplain.png}
  \caption{MLExplain}
  \label{fig:mlexplain}
\end{figure*}

@@

We give some statistics about the project in Figure~\ref{fig:statistics}. As can
be seen, the largest part of the code is the frontend, in particular the
conversion from OCaml's AST to our format. The interpreter is quite short,
because the execution of OCaml is actually very simple. Note that we support all
of OCaml, with the exception of objects and record patterns.

@@

As future work, we plan to extend the subset of OCaml supported by our compiler,
to be able to directly use the standard library when writing interpreters. We
also plan to implement the few OCaml construct missing from our interpreter for
lack of time, such as record patterns and objects. It would be most useful to
document the evaluation order of every OCaml construction to make sure our
interpreters follows it. Finally, be want to improve the web interface and to
allow the user to load code from multiple files.

>>>>

Fortunately the web interface is very simple. It is composed of some auxiliary
JavaScript files, the main JavaScript file -- \texttt{navig-driver.js} --
containing the logic of the application and the corresponding HTML page. The
only modified file is \texttt{navig-driver.js}. The resulting tool can be tested
online\footnote{\url{https://docteur-lalla.github.io/mlexplain/branch/master/driver.html}}
and is shown in Figure~\ref{fig:mlexplain}. The top-left panel shows the
interpreted program, here a simple eval function using GADTs, with the state of the
program depicted on the right. The bottom panel shows the
interpreter, with its state below. One can see that at this point the
\texttt{eval} identifier is being evaluated, with the values of \texttt{r},
\texttt{l}, and \texttt{b} shown on the right.

\begin{figure*}
  \centering
  \includegraphics[width=17cm]{mlexplain.png}
  \caption{MLExplain}
  \label{fig:mlexplain}
\end{figure*}

@@

We give some statistics about the project in Figure~\ref{fig:statistics}. As can
be seen, the largest part of the code is the frontend, in particular the
conversion from OCaml's AST to our format. The interpreter is quite short,
because the execution of OCaml is actually very simple. Note that we support all
of OCaml, with the exception of objects and record patterns, which we have not
had the time to implement.

@@

As future work, we plan to extend the subset of OCaml supported by our compiler,
to be able to directly use the standard library when writing interpreters. We
also plan to implement the few OCaml constructs missing from our interpreter. In
addition, it would be most useful to document the evaluation order of every
OCaml construction to make sure our interpreters follows it. Finally, we want to
improve the web interface and to allow the user to load code from multiple
files.
